Self Regulation Ontology Retest Analyses

### 2018-04-09 code/SRO_Retest_Analyses.Rmd
refactoring

test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_02-03-2018/'

retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-03-2018/'
```

@@

@@

```{r warning=FALSE, message=FALSE}
lit_review = lit_review %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)]),
         type = as.character(type)) %>%
  mutate(task_group = gsub("_", " ", task_group),
         var = gsub("_", " ", var)) %>%
  arrange(task_group, raw_fit, var) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group)) %>%
    select(-measure_description, -reference)
```

@@

```{r echo=FALSE}
rm(tmp, comb)
```

@@

```{r}
var_boot_df = boot_df %>%
  group_by(dv) %>%
  summarise(mean_icc = mean(icc))

@@

Model comparisons building model to predict the reliabilities in the literature from our results.

@@

  mod_lit = lm(retest_reliability ~ lit_predictor+scale(sample_size), data=sampled_df)
  mod_boot = lm(retest_reliability ~ mean_icc+scale(sample_size), data=sampled_df)

  out = data.frame(r2_lit = summary(mod_lit)$r.squared,
                   r2_boot = summary(mod_boot)$r.squared,
                   m_lit = coef(summary(mod_lit))["lit_predictor","Estimate"],
                   m_boot = coef(summary(mod_boot))["mean_icc","Estimate"])

@@

comp_lit_pred_out = plyr::rdply(1000, comp_lit_pred(rel_comp))

comp_lit_pred_out %>%
  select(-.n) %>%
  gather(key, value) %>%
  separate(key, c("stat", "sample"), sep = "_") %>%
  ggplot(aes(value, fill=sample))+
  geom_density(alpha = 0.5, position='identity')+
  facet_wrap(~stat, scales='free')+
  theme(legend.title = element_blank())+
  xlab('')
```

```{r}
with(comp_lit_pred_out, t.test(r2_lit, r2_boot))
```

```{r}
mod1 = lmer(retest_reliability ~ mean_icc + (1|dv), data=rel_comp)
mod1a = lm(retest_reliability ~ mean_icc, data=rel_comp)

cor(predict(mod1), rel_comp$retest_reliability)^2
cor(predict(mod1a), rel_comp$retest_reliability)^2

# mod2 = lmer(retest_reliability ~ mean_icc + (mean_icc|dv), data=rel_comp)

rel_comp %>%
  select(dv, retest_reliability, mean_icc)

summary(mod1a)

summary(lm(retest_reliability ~ mean_icc*scale(sample_size), data=rel_comp))

```{r}
rel_comp %>%
  ggplot()+  
  geom_boxplot(aes(mean_icc, retest_reliability, group=dv))+
  geom_smooth(aes(mean_icc, retest_reliability), method= 'lm')+
  theme_bw()+
  theme(legend.position = 'none')+
  geom_abline(slope=1, intercept=0)+
  geom_abline(slope=0, intercept=0.3, linetype='dashed')+
  xlim(-0.2, 1)+
  ylim(-0.2, 1)+
  # facet_grid(task~.)+
  xlab('Mean bootstrapped ICC')+
  ylab('Reliability estimate from literature')

NOTE: not all metrics are ICC's

```{r echo=FALSE}
rm(tmp, rel_comp, boot_comp, d_boot, d_lit, mod1, mod2, mod3, mod4, n_df, m1, m2, var1, var2, sd_pooled, task, i, n1, n2)
```

@@

```{r message=FALSE, warning=FALSE}

boot_df %>%
  group_by(dv) %>%
  summarise(icc_median = quantile(icc, probs = 0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            spearman_median = quantile(spearman, probs = 0.5),
            spearman_2.5 = quantile(spearman, probs = 0.025),
            spearman_97.5 = quantile(spearman, probs = 0.975)) %>%
  datatable() %>%
  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
```

>>>>

test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_03-29-2018/'

retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-29-2018/'
```

@@

```{r message=FALSE}
lit_review = lit_review %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)]),
         type = as.character(type)) %>%
  mutate(task_group = gsub("_", " ", task_group),
         var = gsub("_", " ", var)) %>%
  arrange(task_group, raw_fit, var) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group)) %>%
  select(-measure_description)

tmp = lit_review[duplicated(lit_review$reference)==FALSE,]

nrow(tmp)
sum(tmp$sample_size)
nrow(lit_review)
```

```{r}
rm(tmp)
```

@@

```{r warning=FALSE, message=FALSE}
lit_review = lit_review %>%
  select(-reference)
```

@@

```{r echo=FALSE}
rm(tmp, comb, sig_days_effect, t1_2_difference, duplicate_items, duplicate_items_data_t1, duplicate_items_data_t2, extract_items, get_delay_effect)
```

@@

```{r message=FALSE}
var_boot_df = boot_df %>%
  group_by(dv) %>%
  summarise(mean_icc = mean(icc),
            mean_pearson = mean(pearson))

@@

### Noise ceiling

Model comparisons building model to predict the reliabilities in the literature from a sample from our results versus a sample form the literature.

@@

  mod_lit = lm(retest_reliability ~ lit_predictor+scale(sample_size)+task, data=sampled_df)
  mod_boot = lm(retest_reliability ~ mean_pearson+scale(sample_size)+task, data=sampled_df)

  out = data.frame(r2_lit = summary(mod_lit)$r.squared,
                   r2_boot = summary(mod_boot)$r.squared,
                   m_lit = coef(summary(mod_lit))["lit_predictor","Estimate"],
                   m_boot = coef(summary(mod_boot))["mean_pearson","Estimate"])

@@

comp_lit_pred_out = plyr::rdply(1000, comp_lit_pred(rel_comp))
```

```{r}
tmp = comp_lit_pred_out %>%
  select(-.n) %>%
  gather(key, value) %>%
  separate(key, c("stat", "sample"), sep = "_")

tmp$stat = as.factor(tmp$stat)
levels(tmp$stat) <- c("coefficient", expression(r^"2"))

tmp %>%  
  ggplot(aes(value, fill=sample))+
  geom_density(alpha = 0.5, position='identity', color=NA)+
  facet_grid(.~stat, scales='free', labeller = label_parsed)+
  scale_fill_discrete(breaks=c("boot","lit"),
                       labels=c("Empirical", "Literature"),
                      name="Prediction")+
  xlab('')+
  ylab('')

ggsave('Lit_Noise_Ceiling.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 10, height = 4, units = "in", limitsize = FALSE, dpi = 100)
```

```{r}
with(comp_lit_pred_out, t.test(r2_lit, r2_boot, paired=T))
```

```{r}
with(comp_lit_pred_out, t.test(m_lit, m_boot))
```

```{r echo=FALSE}
rm(tmp, rel_comp, boot_comp, mod1, mod2, mod3, mod4, n_df, i, lit_emp_cor, lit_emp_cor_out, comp_lit_pred, comp_lit_pred_out)
```

@@

```{r message=FALSE, warning=FALSE}
boot_df %>%
  group_by(dv) %>%
  summarise(icc_median = quantile(icc, probs = 0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            spearman_median = quantile(spearman, probs = 0.5),
            spearman_2.5 = quantile(spearman, probs = 0.025),
            spearman_97.5 = quantile(spearman, probs = 0.975)) %>%
  datatable() %>%
  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
```
